### 2019-12-02 inst/README.rmd
updating README and .travis removes provR reference

- [Rclean](https://github.com/MKLau/Rclean) was created to help
  scientists more *easily* write "cleaner" code. 
- Written with research scientists that are results oriented in mind,
  the package's primary function provides a simple way to isolate the
  minimal code you need to produce a specific result, such as a
  statistical table or a figure.
- By focusing on specific results (aka. variables), large and/or
  complicated analytical scripts can be paired down to the essentials
  and easily re-factored to be more robust and easily shared.

>>>>

- [Rclean](https://github.com/ProvTools/Rclean) was created to help
    scientists more *easily* write “cleaner” code.
- Written with research scientists that are results oriented in mind,
    the package’s primary function provides a simple way to isolate
    the minimal code you need to produce a specific result, such as a
    statistical table or a figure. By focusing on specific results
    (aka. variables), large and/or complicated analytical scripts can
    be paired down to the essentials and easily re-factored to be more
    robust and easily shared.
- The following is a brief introduction to the package. For more
  details, see `vignette("Rclean")`.
